Comparing distance distributions for top predictive features between bins with and without TADs

### 2019-05-20 Scripts/comparing_distance_profiles_using_density_plots.Rmd
editted results script

## 10kb

```{r}
train <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/training_testing/train.rds"))

enetcoefs <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds"))

names(train) <- gsub(paste(c("`", 
                             "Gm12878", 
                             "-", 
                             #"_", 
                             #"dist", "count", "perc",
                             "Haib", 
                             "Sydh",
                             "Uta",
                             "Uw",
                             "Broad",
                             "Uchicago"), collapse = "|"), "", names(train))
train <- train[,c(1,which(names(train) %in% enetcoefs))]

set.seed(123)
train_smote <- SMOTE(y ~ ., 
                     data=train, 
                     perc.over = 100, 
                     perc.under = 200)

@@

### Top Annotations

####SMC

```{r}
annotname <- gsub(paste(c("`", 
             "Gm12878", 
             "-", 
             #"_", 
             #"dist", "count", "perc",
             "Haib", 
             "Sydh",
             "Uta",
             "Uw",
             "Broad",
             "Uchicago"), collapse = "|"), "", "Gm12878-Smc3ab9263-Sydh_dist")

annotdata.smc <- train_smote[, c(1, which(names(train_smote)==annotname))]

#ks.test(annotdata.smc[which(annotdata.smc$y=="No"),2], annotdata.smc[which(annotdata.smc$y=="Yes"),2], alternative = "two.sided")

perm.pval <- pvalue(oneway_test(annotdata.smc[,2] ~ annotdata.smc[,1],
                     data=annotdata.smc,
                     alternative="greater", 
                     distribution=approximate(B=10000)))[1]

perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))

plottitle <- paste(gsub(paste(c("Gm12878",
                                  "-","_",
                                  "dist","perc","count",
                                  "Haib",
                                  "Sydh",
                                  "Uta",
                                  "Uw",
                                  "Broad",
                                  "Uchicago"), 
                                collapse = "|"), 
                          "",
                          "Gm12878-Smc3ab9263-Sydh_dist"))

p.gm12878.10kb.smc <- ggplot(annotdata.smc, aes(x=Smc3ab9263_dist, color=y)) +
    geom_density() +
    scale_color_discrete(name="Class of\nGenomic Bin",
                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
    ylab("") +
    xlab("") +
    ggtitle("SMC3a\nPermutation P-Value: < 0.0001") +
    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
    theme_bw() +
    theme(axis.text.x = element_text(size=15 #,
                                     #angle = 45, 
                                     #margin = ggplot2::margin(t = 35),
                                     #hjust = 1
    ),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    legend.text=element_text(size=15),
    legend.title=element_text(size=20),
    plot.title = element_text(size=20,
                              hjust=.5))
```

####ZNF143

```{r}
annotname <- gsub(paste(c("`", 
             "Gm12878", 
             "-", 
             #"_", 
             #"dist", "count", "perc",
             "Haib", 
             "Sydh",
             "Uta",
             "Uw",
             "Broad",
             "Uchicago"), collapse = "|"), "", "Gm12878-Znf143166181ap-Sydh_dist")

annotdata.znf143 <- train_smote[, c(1, which(names(train_smote)==annotname))]

#ks.test(annotdata.znf143[which(annotdata.znf143$y=="No"),2], annotdata.znf143[which(annotdata.znf143$y=="Yes"),2], alternative = "two.sided")

perm.pval <- pvalue(oneway_test(annotdata.znf143[,2] ~ annotdata.znf143[,1],
                     data=annotdata.znf143,
                     alternative="greater", 
                     distribution=approximate(B=10000)))[1]

perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))

plottitle <- paste(gsub(paste(c("Gm12878",
                                  "-","_",
                                  "dist","perc","count",
                                  "Haib",
                                  "Sydh",
                                  "Uta",
                                  "Uw",
                                  "Broad",
                                  "Uchicago"), 
                                collapse = "|"), 
                          "",
                          "Gm12878-Znf143166181ap-Sydh_dist"))

p.gm12878.10kb.znf143 <- ggplot(annotdata.znf143, aes(x=Znf143166181ap_dist, color=y)) +
    geom_density() +
    scale_color_discrete(name="Class of\nGenomic Bin",
                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
    ylab("") +
    xlab("") +
    ggtitle("ZNF143\nPermutation P-Value: < 0.0001") +
    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
    theme_bw() +
    theme(axis.text.x = element_text(size=15 #,
                                     #angle = 45, 
                                     #margin = ggplot2::margin(t = 35),
                                     #hjust = 1
    ),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    legend.text=element_text(size=15),
    legend.title=element_text(size=20),
    plot.title = element_text(size=20,
                              hjust=.5))
```

####CTCF

```{r}
annotname <- gsub(paste(c("`", 
             "Gm12878", 
             "-", 
             #"_", 
             #"dist", "count", "perc",
             "Haib", 
             "Sydh",
             "Uta",
             "Uw",
             "Broad",
             "Uchicago"), collapse = "|"), "", "Gm12878-Ctcf-Broad_dist")

annotdata.ctcf <- train_smote[, c(1, which(names(train_smote)==annotname))]

#ks.test(annotdata.ctcf[which(annotdata.ctcf$y=="No"),2], annotdata.ctcf[which(annotdata.ctcf$y=="Yes"),2], alternative = "two.sided")

perm.pval <- pvalue(oneway_test(annotdata.ctcf[,2] ~ annotdata.ctcf[,1],
                     data=annotdata.ctcf,
                     alternative="greater", 
                     distribution=approximate(B=10000)))[1]

perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))

plottitle <- paste(gsub(paste(c("Gm12878",
                                  "-","_",
                                  "dist","perc","count",
                                  "Haib",
                                  "Sydh",
                                  "Uta",
                                  "Uw",
                                  "Broad",
                                  "Uchicago"), 
                                collapse = "|"), 
                          "",
                          "Gm12878-Ctcf-Broad_dist"))

p.gm12878.10kb.ctcf <- ggplot(annotdata.ctcf, aes(x=Ctcf_dist, color=y)) +
    geom_density() +
    scale_color_discrete(name="Class of\nGenomic Bin",
                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
    ylab("") +
    xlab("") +
    ggtitle("CTCF\nPermutation P-Value: < 0.0001") +
    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
    theme_bw() +
    theme(axis.text.x = element_text(size=15 #,
                                     #angle = 45, 
                                     #margin = ggplot2::margin(t = 35),
                                     #hjust = 1
    ),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    legend.text=element_text(size=15),
    legend.title=element_text(size=20),
    plot.title = element_text(size=20,
                              hjust=.5))
```

####RAD21

```{r}
annotname <- gsub(paste(c("`", 
             "Gm12878", 
             "-", 
             #"_", 
             #"dist", "count", "perc",
             "Haib", 
             "Sydh",
             "Uta",
             "Uw",
             "Broad",
             "Uchicago"), collapse = "|"), "", "Gm12878-Rad21-Haib_dist")

annotdata.rad21 <- train_smote[, c(1, which(names(train_smote)==annotname))]

#ks.test(annotdata.rad21[which(annotdata.rad21$y=="No"),2], annotdata.rad21[which(annotdata.rad21$y=="Yes"),2], alternative = "two.sided")

perm.pval <- pvalue(oneway_test(annotdata.rad21[,2] ~ annotdata.rad21[,1],
                     data=annotdata.rad21,
                     alternative="greater", 
                     distribution=approximate(B=10000)))[1]

perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))

plottitle <- paste(gsub(paste(c("Gm12878",
                                  "-","_",
                                  "dist","perc","count",
                                  "Haib",
                                  "Sydh",
                                  "Uta",
                                  "Uw",
                                  "Broad",
                                  "Uchicago"), 
                                collapse = "|"), 
                          "",
                          "Gm12878-Rad21-Haib_dist"))

p.gm12878.10kb.rad21 <- ggplot(annotdata.rad21, aes(x=Rad21_dist, color=y)) +
    geom_density() +
    scale_color_discrete(name="Class of\nGenomic Bin",
                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
    ylab("") +
    xlab("") +
    ggtitle("RAD21\nPermutation P-Value: < 0.0001") +
    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
    theme_bw() +
    theme(axis.text.x = element_text(size=15 #,
                                     #angle = 45, 
                                     #margin = ggplot2::margin(t = 35),
                                     #hjust = 1
    ),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    legend.text=element_text(size=15),
    legend.title=element_text(size=20),
    plot.title = element_text(size=20,
                              hjust=.5))
```

## 25kb

```{r}
train <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/25kb/training_testing/train.rds"))

enetcoefs <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds"))

names(train) <- gsub(paste(c("`", 
                             "Gm12878", 
                             "-", 
                             #"_", 
                             #"dist", "count", "perc",
                             "Haib", 
                             "Sydh",
                             "Uta",
                             "Uw",
                             "Broad",
                             "Uchicago"), collapse = "|"), "", names(train))
train <- train[,c(1,which(names(train) %in% enetcoefs))]

set.seed(123)
train_smote <- SMOTE(y ~ ., 
                     data=train, 
                     perc.over = 100, 
                     perc.under = 200)

@@

### Top Annotations

####SMC

```{r}
annotname <- gsub(paste(c("`", 
             "Gm12878", 
             "-", 
             #"_", 
             #"dist", "count", "perc",
             "Haib", 
             "Sydh",
             "Uta",
             "Uw",
             "Broad",
             "Uchicago"), collapse = "|"), "", "Gm12878-Smc3ab9263-Sydh_dist")

annotdata.smc <- train_smote[, c(1, which(names(train_smote)==annotname))]

#ks.test(annotdata.smc[which(annotdata.smc$y=="No"),2], annotdata.smc[which(annotdata.smc$y=="Yes"),2], alternative = "two.sided")

perm.pval <- pvalue(oneway_test(annotdata.smc[,2] ~ annotdata.smc[,1],
                     data=annotdata.smc,
                     alternative="greater", 
                     distribution=approximate(B=10000)))[1]

perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))

plottitle <- paste(gsub(paste(c("Gm12878",
                                  "-","_",
                                  "dist","perc","count",
                                  "Haib",
                                  "Sydh",
                                  "Uta",
                                  "Uw",
                                  "Broad",
                                  "Uchicago"), 
                                collapse = "|"), 
                          "",
                          "Gm12878-Smc3ab9263-Sydh_dist"))

p.gm12878.25kb.smc <- ggplot(annotdata.smc, aes(x=Smc3ab9263_dist, color=y)) +
    geom_density() +
    scale_color_discrete(name="Class of\nGenomic Bin",
                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
    ylab("") +
    xlab("") +
    ggtitle("SMC3a\nPermutation P-Value: < 0.0001") +
    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
    theme_bw() +
    theme(axis.text.x = element_text(size=15 #,
                                     #angle = 45, 
                                     #margin = ggplot2::margin(t = 35),
                                     #hjust = 1
    ),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    legend.text=element_text(size=15),
    legend.title=element_text(size=20),
    plot.title = element_text(size=20,
                              hjust=.5))
```

####ZNF143

```{r}
annotname <- gsub(paste(c("`", 
             "Gm12878", 
             "-", 
             #"_", 
             #"dist", "count", "perc",
             "Haib", 
             "Sydh",
             "Uta",
             "Uw",
             "Broad",
             "Uchicago"), collapse = "|"), "", "Gm12878-Znf143166181ap-Sydh_dist")

annotdata.znf143 <- train_smote[, c(1, which(names(train_smote)==annotname))]

#ks.test(annotdata.znf143[which(annotdata.znf143$y=="No"),2], annotdata.znf143[which(annotdata.znf143$y=="Yes"),2], alternative = "two.sided")

perm.pval <- pvalue(oneway_test(annotdata.znf143[,2] ~ annotdata.znf143[,1],
                     data=annotdata.znf143,
                     alternative="greater", 
                     distribution=approximate(B=10000)))[1]

perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))

plottitle <- paste(gsub(paste(c("Gm12878",
                                  "-","_",
                                  "dist","perc","count",
                                  "Haib",
                                  "Sydh",
                                  "Uta",
                                  "Uw",
                                  "Broad",
                                  "Uchicago"), 
                                collapse = "|"), 
                          "",
                          "Gm12878-Znf143166181ap-Sydh_dist"))

p.gm12878.25kb.znf143 <- ggplot(annotdata.znf143, aes(x=Znf143166181ap_dist, color=y)) +
    geom_density() +
    scale_color_discrete(name="Class of\nGenomic Bin",
                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
    ylab("") +
    xlab("") +
    ggtitle("ZNF143\nPermutation P-Value: < 0.0001") +
    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
    theme_bw() +
    theme(axis.text.x = element_text(size=15 #,
                                     #angle = 45, 
                                     #margin = ggplot2::margin(t = 35),
                                     #hjust = 1
    ),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    legend.text=element_text(size=15),
    legend.title=element_text(size=20),
    plot.title = element_text(size=20,
                              hjust=.5))
```

####CTCF

```{r}
annotname <- gsub(paste(c("`", 
             "Gm12878", 
             "-", 
             #"_", 
             #"dist", "count", "perc",
             "Haib", 
             "Sydh",
             "Uta",
             "Uw",
             "Broad",
             "Uchicago"), collapse = "|"), "", "Gm12878-Ctcf-Broad_dist")

annotdata.ctcf <- train_smote[, c(1, which(names(train_smote)==annotname))]

#ks.test(annotdata.ctcf[which(annotdata.ctcf$y=="No"),2], annotdata.ctcf[which(annotdata.ctcf$y=="Yes"),2], alternative = "two.sided")

perm.pval <- pvalue(oneway_test(annotdata.ctcf[,2] ~ annotdata.ctcf[,1],
                     data=annotdata.ctcf,
                     alternative="greater", 
                     distribution=approximate(B=10000)))[1]

perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))

plottitle <- paste(gsub(paste(c("Gm12878",
                                  "-","_",
                                  "dist","perc","count",
                                  "Haib",
                                  "Sydh",
                                  "Uta",
                                  "Uw",
                                  "Broad",
                                  "Uchicago"), 
                                collapse = "|"), 
                          "",
                          "Gm12878-Ctcf-Broad_dist"))

p.gm12878.25kb.ctcf <- ggplot(annotdata.ctcf, aes(x=Ctcf_dist, color=y)) +
    geom_density() +
    scale_color_discrete(name="Class of\nGenomic Bin",
                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
    ylab("") +
    xlab("") +
    ggtitle("CTCF\nPermutation P-Value: < 0.0001") +
    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
    theme_bw() +
    theme(axis.text.x = element_text(size=15 #,
                                     #angle = 45, 
                                     #margin = ggplot2::margin(t = 35),
                                     #hjust = 1
    ),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    legend.text=element_text(size=15),
    legend.title=element_text(size=20),
    plot.title = element_text(size=20,
                              hjust=.5))
```

####RAD21

```{r}
annotname <- gsub(paste(c("`", 
             "Gm12878", 
             "-", 
             #"_", 
             #"dist", "count", "perc",
             "Haib", 
             "Sydh",
             "Uta",
             "Uw",
             "Broad",
             "Uchicago"), collapse = "|"), "", "Gm12878-Rad21-Haib_dist")

annotdata.rad21 <- train_smote[, c(1, which(names(train_smote)==annotname))]

#ks.test(annotdata.rad21[which(annotdata.rad21$y=="No"),2], annotdata.rad21[which(annotdata.rad21$y=="Yes"),2], alternative = "two.sided")

perm.pval <- pvalue(oneway_test(annotdata.rad21[,2] ~ annotdata.rad21[,1],
                     data=annotdata.rad21,
                     alternative="greater", 
                     distribution=approximate(B=10000)))[1]

perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))

plottitle <- paste(gsub(paste(c("Gm12878",
                                  "-","_",
                                  "dist","perc","count",
                                  "Haib",
                                  "Sydh",
                                  "Uta",
                                  "Uw",
                                  "Broad",
                                  "Uchicago"), 
                                collapse = "|"), 
                          "",
                          "Gm12878-Rad21-Haib_dist"))

p.gm12878.25kb.rad21 <- ggplot(annotdata.rad21, aes(x=Rad21_dist, color=y)) +
    geom_density() +
    scale_color_discrete(name="Class of\nGenomic Bin",
                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
    ylab("") +
    xlab("") +
    ggtitle("RAD21\nPermutation P-Value: < 0.0001") +
    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
    theme_bw() +
    theme(axis.text.x = element_text(size=15 #,
                                     #angle = 45, 
                                     #margin = ggplot2::margin(t = 35),
                                     #hjust = 1
    ),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    legend.text=element_text(size=15),
    legend.title=element_text(size=20),
    plot.title = element_text(size=20,
                              hjust=.5))
```

## 50kb

```{r}
train <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/50kb/training_testing/train.rds"))

enetcoefs <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds"))

names(train) <- gsub(paste(c("`", 
                             "Gm12878", 
                             "-", 
                             #"_", 
                             #"dist", "count", "perc",
                             "Haib", 
                             "Sydh",
                             "Uta",
                             "Uw",
                             "Broad",
                             "Uchicago"), collapse = "|"), "", names(train))
train <- train[,c(1,which(names(train) %in% enetcoefs))]

set.seed(123)
train_smote <- SMOTE(y ~ ., 
                     data=train, 
                     perc.over = 100, 
                     perc.under = 200)

@@

### Top Annotations

####SMC

```{r}
annotname <- gsub(paste(c("`", 
             "Gm12878", 
             "-", 
             #"_", 
             #"dist", "count", "perc",
             "Haib", 
             "Sydh",
             "Uta",
             "Uw",
             "Broad",
             "Uchicago"), collapse = "|"), "", "Gm12878-Smc3ab9263-Sydh_dist")

annotdata.smc <- train_smote[, c(1, which(names(train_smote)==annotname))]

#ks.test(annotdata.smc[which(annotdata.smc$y=="No"),2], annotdata.smc[which(annotdata.smc$y=="Yes"),2], alternative = "two.sided")

perm.pval <- pvalue(oneway_test(annotdata.smc[,2] ~ annotdata.smc[,1],
                     data=annotdata.smc,
                     alternative="greater", 
                     distribution=approximate(B=10000)))[1]

perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))

plottitle <- paste(gsub(paste(c("Gm12878",
                                  "-","_",
                                  "dist","perc","count",
                                  "Haib",
                                  "Sydh",
                                  "Uta",
                                  "Uw",
                                  "Broad",
                                  "Uchicago"), 
                                collapse = "|"), 
                          "",
                          "Gm12878-Smc3ab9263-Sydh_dist"))

p.gm12878.50kb.smc <- ggplot(annotdata.smc, aes(x=Smc3ab9263_dist, color=y)) +
    geom_density() +
    scale_color_discrete(name="Class of\nGenomic Bin",
                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
    ylab("") +
    xlab("") +
    ggtitle("SMC3a\nPermutation P-Value: < 0.0001") +
    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
    theme_bw() +
    theme(axis.text.x = element_text(size=15 #,
                                     #angle = 45, 
                                     #margin = ggplot2::margin(t = 35),
                                     #hjust = 1
    ),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    legend.text=element_text(size=15),
    legend.title=element_text(size=20),
    plot.title = element_text(size=20,
                              hjust=.5))
```

####ZNF143

```{r}
annotname <- gsub(paste(c("`", 
             "Gm12878", 
             "-", 
             #"_", 
             #"dist", "count", "perc",
             "Haib", 
             "Sydh",
             "Uta",
             "Uw",
             "Broad",
             "Uchicago"), collapse = "|"), "", "Gm12878-Znf143166181ap-Sydh_dist")

annotdata.znf143 <- train_smote[, c(1, which(names(train_smote)==annotname))]

#ks.test(annotdata.znf143[which(annotdata.znf143$y=="No"),2], annotdata.znf143[which(annotdata.znf143$y=="Yes"),2], alternative = "two.sided")

perm.pval <- pvalue(oneway_test(annotdata.znf143[,2] ~ annotdata.znf143[,1],
                     data=annotdata.znf143,
                     alternative="greater", 
                     distribution=approximate(B=10000)))[1]

perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))

plottitle <- paste(gsub(paste(c("Gm12878",
                                  "-","_",
                                  "dist","perc","count",
                                  "Haib",
                                  "Sydh",
                                  "Uta",
                                  "Uw",
                                  "Broad",
                                  "Uchicago"), 
                                collapse = "|"), 
                          "",
                          "Gm12878-Znf143166181ap-Sydh_dist"))

p.gm12878.50kb.znf143 <- ggplot(annotdata.znf143, aes(x=Znf143166181ap_dist, color=y)) +
    geom_density() +
    scale_color_discrete(name="Class of\nGenomic Bin",
                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
    ylab("") +
    xlab("") +
    ggtitle("ZNF143\nPermutation P-Value: < 0.0001") +
    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
    theme_bw() +
    theme(axis.text.x = element_text(size=15 #,
                                     #angle = 45, 
                                     #margin = ggplot2::margin(t = 35),
                                     #hjust = 1
    ),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    legend.text=element_text(size=15),
    legend.title=element_text(size=20),
    plot.title = element_text(size=20,
                              hjust=.5))
```

####CTCF

```{r}
annotname <- gsub(paste(c("`", 
             "Gm12878", 
             "-", 
             #"_", 
             #"dist", "count", "perc",
             "Haib", 
             "Sydh",
             "Uta",
             "Uw",
             "Broad",
             "Uchicago"), collapse = "|"), "", "Gm12878-Ctcf-Broad_dist")

annotdata.ctcf <- train_smote[, c(1, which(names(train_smote)==annotname))]

#ks.test(annotdata.ctcf[which(annotdata.ctcf$y=="No"),2], annotdata.ctcf[which(annotdata.ctcf$y=="Yes"),2], alternative = "two.sided")

perm.pval <- pvalue(oneway_test(annotdata.ctcf[,2] ~ annotdata.ctcf[,1],
                     data=annotdata.ctcf,
                     alternative="greater", 
                     distribution=approximate(B=10000)))[1]

perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))

plottitle <- paste(gsub(paste(c("Gm12878",
                                  "-","_",
                                  "dist","perc","count",
                                  "Haib",
                                  "Sydh",
                                  "Uta",
                                  "Uw",
                                  "Broad",
                                  "Uchicago"), 
                                collapse = "|"), 
                          "",
                          "Gm12878-Ctcf-Broad_dist"))

p.gm12878.50kb.ctcf <- ggplot(annotdata.ctcf, aes(x=Ctcf_dist, color=y)) +
    geom_density() +
    scale_color_discrete(name="Class of\nGenomic Bin",
                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
    ylab("") +
    xlab("") +
    ggtitle("CTCF\nPermutation P-Value: < 0.0001") +
    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
    theme_bw() +
    theme(axis.text.x = element_text(size=15 #,
                                     #angle = 45, 
                                     #margin = ggplot2::margin(t = 35),
                                     #hjust = 1
    ),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    legend.text=element_text(size=15),
    legend.title=element_text(size=20),
    plot.title = element_text(size=20,
                              hjust=.5))
```

>>>>

## Top annotations

```{r}
annots <- c("Gm12878-Smc3ab9263-Sydh_dist",
            "Gm12878-Ctcf-Broad_dist",
            "Gm12878-Znf143166181ap-Sydh_dist",
            "Gm12878-Yy1sc281-Haib_dist",
            "Gm12878-Rad21-Haib_dist")
```

### 10kb

```{r}

dist_list_gm12878_10kb <- list()

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  whole_genome_dat <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/gm12878_10kb.rds")

	  binslist_dat <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/binslist10.rds")

	  reduce_chr <- tolower(chrs[i])
	  chr_specific_dat <- whole_genome_dat[which(as.character(seqnames(binslist_dat))==reduce_chr),
	                                       c(1, which(names(whole_genome_dat) %in% annots))]

	  set.seed(123)
	  inTrainingSet <- sample(length(chr_specific_dat$y),floor(length(chr_specific_dat$y)*.7))
    train <- chr_specific_dat[inTrainingSet,]

    set.seed(123)
	  train <- SMOTE(y ~ ., 
	                 data=train, 
                   perc.over = 100, 
                   perc.under = 200)
	  train$CHR <- chrs[i]
	  train$Resolution <- "10 kb"

	  dist_list_gm12878_10kb[[i]] <- train

}

dist_gm12878_10kb <- do.call("rbind", dist_list_gm12878_10kb)

#dist_gm12878_10kb_summ <- dist_gm12878_10kb %>%
#  dplyr::group_by(y,CHR) %>%
#  dplyr::summarise(Ctcf = mean(`Gm12878-Ctcf-Broad_dist`, na.rm = TRUE),
#                   Rad21 = mean(`Gm12878-Rad21-Haib_dist`, na.rm = TRUE),
#                   Smc3ab9263 = mean(`Gm12878-Smc3ab9263-Sydh_dist`, na.rm = TRUE),
#                   Yy1sc281 = mean(`Gm12878-Yy1sc281-Haib_dist`, na.rm = TRUE),
#                   Znf143166181ap = mean(`Gm12878-Znf143166181ap-Sydh_dist`, na.rm = TRUE))

@@

### 25kb

```{r}

dist_list_gm12878_25kb <- list()

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  whole_genome_dat <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/gm12878_25kb.rds")

	  binslist_dat <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/binslist25.rds")

	  reduce_chr <- tolower(chrs[i])
	  chr_specific_dat <- whole_genome_dat[which(as.character(seqnames(binslist_dat))==reduce_chr),
	                                       c(1, which(names(whole_genome_dat) %in% annots))]

	  set.seed(123)
	  inTrainingSet <- sample(length(chr_specific_dat$y),floor(length(chr_specific_dat$y)*.7))
    train <- chr_specific_dat[inTrainingSet,]

    set.seed(123)
	  train <- SMOTE(y ~ ., 
	                 data=train, 
                   perc.over = 100, 
                   perc.under = 200)
	  train$CHR <- chrs[i]
	  train$Resolution <- "25 kb"

	  dist_list_gm12878_25kb[[i]] <- train

}

dist_gm12878_25kb <- do.call("rbind", dist_list_gm12878_25kb)

#dist_gm12878_25kb_summ <- dist_gm12878_25kb %>%
#  dplyr::group_by(y,CHR) %>%
#  dplyr::summarise(Ctcf = mean(`Gm12878-Ctcf-Broad_dist`, na.rm = TRUE),
#                   Rad21 = mean(`Gm12878-Rad21-Haib_dist`, na.rm = TRUE),
#                   Smc3ab9263 = mean(`Gm12878-Smc3ab9263-Sydh_dist`, na.rm = TRUE),
#                   Yy1sc281 = mean(`Gm12878-Yy1sc281-Haib_dist`, na.rm = TRUE),
#                   Znf143166181ap = mean(`Gm12878-Znf143166181ap-Sydh_dist`, na.rm = TRUE))

@@

### 50kb

```{r}

dist_list_gm12878_50kb <- list()

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  whole_genome_dat <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/gm12878_50kb.rds")

	  binslist_dat <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/binslist50.rds")

	  reduce_chr <- tolower(chrs[i])
	  chr_specific_dat <- whole_genome_dat[which(as.character(seqnames(binslist_dat))==reduce_chr),
	                                       c(1, which(names(whole_genome_dat) %in% annots))]

	  set.seed(123)
	  inTrainingSet <- sample(length(chr_specific_dat$y),floor(length(chr_specific_dat$y)*.7))
    train <- chr_specific_dat[inTrainingSet,]

    set.seed(123)
	  train <- SMOTE(y ~ ., 
	                 data=train, 
                   perc.over = 100, 
                   perc.under = 200)
	  train$CHR <- chrs[i]
	  train$Resolution <- "50 kb"

	  dist_list_gm12878_50kb[[i]] <- train

}

dist_gm12878_50kb <- do.call("rbind", dist_list_gm12878_50kb)

#dist_gm12878_50kb_summ <- dist_gm12878_50kb %>%
#  dplyr::group_by(y,CHR) %>%
#  dplyr::summarise(Ctcf = mean(`Gm12878-Ctcf-Broad_dist`, na.rm = TRUE),
#                   Rad21 = mean(`Gm12878-Rad21-Haib_dist`, na.rm = TRUE),
#                   Smc3ab9263 = mean(`Gm12878-Smc3ab9263-Sydh_dist`, na.rm = TRUE),
#                   Yy1sc281 = mean(`Gm12878-Yy1sc281-Haib_dist`, na.rm = TRUE),
#                   Znf143166181ap = mean(`Gm12878-Znf143166181ap-Sydh_dist`, na.rm = TRUE))

@@

### 100kb

```{r}

dist_list_gm12878_100kb <- list()

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  whole_genome_dat <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/gm12878_100kb.rds")

	  binslist_dat <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/binslist100.rds")

	  reduce_chr <- tolower(chrs[i])
	  chr_specific_dat <- whole_genome_dat[which(as.character(seqnames(binslist_dat))==reduce_chr),
	                                       c(1, which(names(whole_genome_dat) %in% annots))]

	  set.seed(123)
	  inTrainingSet <- sample(length(chr_specific_dat$y),floor(length(chr_specific_dat$y)*.7))
    train <- chr_specific_dat[inTrainingSet,]

    set.seed(123)
	  train <- SMOTE(y ~ ., 
	                 data=train, 
                   perc.over = 100, 
                   perc.under = 200)
	  train$CHR <- chrs[i]
	  train$Resolution <- "100 kb"

	  dist_list_gm12878_100kb[[i]] <- train

}

dist_gm12878_100kb <- do.call("rbind", dist_list_gm12878_100kb)

#dist_gm12878_100kb_summ <- dist_gm12878_100kb %>%
#  dplyr::group_by(y,CHR) %>%
#  dplyr::summarise(Ctcf = mean(`Gm12878-Ctcf-Broad_dist`, na.rm = TRUE),
#                   Rad21 = mean(`Gm12878-Rad21-Haib_dist`, na.rm = TRUE),
#                   Smc3ab9263 = mean(`Gm12878-Smc3ab9263-Sydh_dist`, na.rm = TRUE),
#                   Yy1sc281 = mean(`Gm12878-Yy1sc281-Haib_dist`, na.rm = TRUE),
#                   Znf143166181ap = mean(`Gm12878-Znf143166181ap-Sydh_dist`, na.rm = TRUE))
